### 2015-01-14 fundamentals/impl.tex
he did not epitomize it at all. he expressed it, articulated it, spoke of it. Babbage was neither garbage in nor garbage out
gets rid of overly informal discussion of software nerd debates

Simulation science - like experimental science - has since the beginning had the 
problem of identifying trustworthy results from nonsensical results or noise.
This is epitomized by Charles Babbage, ``On two occasions I have been asked, 
`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right 
answers come out?' ... I am not able rightly to apprehend the kind of confusion 
of ideas that could provoke such a question.'' \cite{babbage_passages_2011}. 
A simulator must both guard against the \emph{garbage in, garbage out} phenomenon, and also assure correctness.

@@

In any multi-person software project, there is a tension between how individuals
wish to write code. Every person tends to have their own custom style. To remedy this,
coding style guides are the software analogy to those for written language,
such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the 
Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
This means that all developers of \Cyclus nominally write \Cyclus code in the same 
way.  This homogenization may be a hurdle to new developers but ultimately 
improves code legibility. Adoption of a single style guide also settles
timeless arguments over what style is `the best.' Having only one means that 
there is a common enemy for all developers to dislike equally.

>>>>

Simulation science - like experimental science - has since the beginning had the 
problem of identifying trustworthy results from nonsensical results or noise.
Charles Babbage famously articulated this, ``On two occasions I have been asked, 
`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right 
answers come out?' ... I am not able rightly to apprehend the kind of confusion 
of ideas that could provoke such a question.'' \cite{babbage_passages_2011}. 
A simulator must both guard against the \emph{garbage in, garbage out} phenomenon, and also assure correctness.

@@

In any multi-person software project, there is a tension between how individuals
wish to write code. Every person tends to have their own custom style. To remedy this,
coding style guides are the software analogy to those for written language,
such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the 
Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
This means that all developers of \Cyclus nominally write \Cyclus code in the same 
way.  This homogenization may be a hurdle to new developers but ultimately 
improves code legibility and, therefore, robustness \cite{cohen_modern_2010}.
